---
title: "Open Government Data, provided by Canton Zurich"
date: "2024-11-13"
output: html_document
---

## Dataset: Nationalratswahlen: Wähleranteil FGA/AL/PDA [%]

Wähleranteil aller Listen der Parteien FGA/AL/PDA bei den Nationalratswahlen

[Direct data shop link for dataset](https://www.zh.ch/de/politik-staat/statistik-daten/datenkatalog.html#/datasets/11@statistisches-amt-kanton-zuerich)

Auto generated R starter code for data set 11@statistisches-amt-kanton-zuerich.

## Metadata

- **Issued** `2016-01-20T20:16:00`
- **Modified** `2023-11-28T15:46:25`
- **Startdate** `2007-12-31`
- **Enddate** `2023-12-31`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/GOVE']`
- **Keyword** `['bezirke', 'gemeinden', 'kanton_zuerich', 'nationalratswahlen', 'parteien', 'politik', 'wahlen', 'ogd']`
- **Publisher** `['Statistisches Amt des Kantons Zürich']`
- **Landingpage** `https://www.zh.ch/de/politik-staat/gemeinden/gemeindeportraet.html`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 10
# Title                    : Nationalratswahlen: Wähleranteil FGA/AL/PDA [%]
# Description              : None
# Issued                   : 2016-01-21T16:30:35
# Modified                 : 2023-11-28T15:46:48

df <- read_delim('https://www.web.statistik.zh.ch/ogd/data/KANTON_ZUERICH_440.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt des Kantons Zürich | Data Shop | datashop@statistik.zh.ch
