---
title: "Open Government Data, provided by Canton Zurich"
date: "2023-09-04"
output: html_document
---

## Dataset: Apotheken [pro 1000 Einw.]

Definition: Alle öffentlichen Apotheken im Kanton Zürich. Aktuellstes Jahr provisorisch. Stand: Anfangs Folgejahr.

[Direct data shop link for dataset](https://www.zh.ch/de/politik-staat/opendata.html#/datasets/234@statistisches-amt-kanton-zuerich)

Auto generated R starter code for data set 234@statistisches-amt-kanton-zuerich.

## Metadata

- **Issued** `2016-01-20T20:16:00`
- **Modified** `2023-04-28T12:54:12`
- **Startdate** `1990-12-31`
- **Enddate** `2022-12-31`
- **Theme** `['Gesundheit']`
- **Keyword** `['apotheken', 'bezirke', 'gemeinden', 'gewerbe', 'kanton_zuerich', 'ogd']`
- **Publisher** `['Statistisches Amt des Kantons Zürich']`
- **Landingpage** `https://www.zh.ch/de/politik-staat/gemeinden/gemeindeportraet.html`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 196
# Title                    : Apotheken [pro 1000 Einw.]
# Description              : None
# Issued                   : 2016-01-21T16:30:35
# Modified                 : 2023-04-28T12:54:12
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://www.web.statistik.zh.ch/ogd/data/KANTON_ZUERICH_547.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Statistisches Amt des Kantons Zürich | Data Shop | datashop@statistik.zh.ch
