---
title: "Open government data provided by Canton of Zurich"
date: "2026-09-27"
output: html_document
---

## Dataset: Baugesuche im Kanton Zürich

In diesen Daten finden Sie sämtliche Bauvorhaben, die im Kanton Zürich beantragt wurden. Die Daten werden im Kanton Zürich erfasst, da für jedes Bauvorhaben ein Baugesuch eingereicht werden muss. Seit 2019 werden diese Gesuche ausschließlich in digitaler Form veröffentlicht.  Die Fach- und Koordinationsstelle OGD (FK OGD) sammelt diese Daten allerdings erst seit dem Herbst 2024, wobei Bauvorhaben mit einigen Ausnahmen bloss ein Jahr in der Datenbank des Amtsblatts öffentlich einsehbar sind. Als Grundlage dafür dienen die Informationen der Gemeinden. Diese erfassen die Baueingaben und übermitteln sie direkt über eine Schnittstelle an die digitale Version des Amtsblatts (siehe "Landing Page"), wo sie gesammelt und der Öffentlichkeit zugänglich gemacht werden. Damit diese Baugesuche in diesem OGD-Datensatz in einer einzelnen Datei bereit gestellt werden können, prüft die FK OGD täglich und automatisiert, ob es neue Baugesuche gegeben hat und fügt allfällige neue Bauvorhaben dem bestehenden Datensatz hinzu. Dabei dienen die Baugesuche nicht nur der Informations- und Dokumentationsfunktion, sondern bilden auch die Grundlage für mögliche Rekurse. Das blosse Baugesuch sagt jedoch nichts darüber aus, was effektiv gebaut wird und es ist mit den vorhandenen Daten nicht möglich, nachzuvollziehen, ob ein Projekt umgesetzt wurde.

Die original Gesuche enthalten genaue Information zu natürlichen und juristischen Personen wie z.B. den Gesuchsstellenden oder der Bauherrschaft. Informationen wie Namen oder Adressen werden in diesen Datensatz jedoch bewusst entfernt. Projektstandorte inkl. BFS- und Kataster-Nummer und Projektbeschriebe werden beibehalten.

[View this dataset in the data catalogue](https://www.zh.ch/de/politik-staat/statistik-daten/datenkatalog.html#/datasets/2982@statistisches-amt-kanton-zuerich)

Automatically generated R starter code for dataset 2982@statistisches-amt-kanton-zuerich.

## Metadata

- **Issued** `2025-06-24T22:00:00`
- **Modified** `2026-09-27T01:59:23`
- **Startdate** `2024-02-06`
- **Enddate** `2026-09-27`
- **Theme** `['http://publications.europa.eu/resource/authority/data-theme/GOVE', 'http://publications.europa.eu/resource/authority/data-theme/REGI']`
- **Keyword** `['bautaetigkeit', 'bauvorhaben', 'bauzonen', 'gemeinden', 'gemeindeverwaltung', 'infrastruktur', 'landparzellen', 'ogd', 'umbau', 'wohnbautaetigkeit', 'wohnungsbau']`
- **Publisher** `['Amt für Statistik und Daten']`
- **Landingpage** `nan`


## Load packages

This template targets tidyverse (2.x) and skimr (2.x) with R 4.1 or newer for the native `|>` pipe; package versions are not pinned. Install missing packages once with `install.packages(c("tidyverse", "skimr"))`.

```{r setup, message=FALSE}
library(tidyverse)
library(skimr)
theme_set(theme_minimal())

get_dataset <- function(url, delim = NULL, drop_empty_unnamed = TRUE, ...) {
  data <- read_delim(url, delim = delim, show_col_types = FALSE, ...)
  stop_for_problems(data)
  if (drop_empty_unnamed && nrow(data) > 0) {
    # Blank CSV headers (often from trailing separators) become "...n".
    unnamed <- grepl("^\\.\\.\\.[0-9]+$", names(data))
    empty_unnamed <- unnamed & map_lgl(data, ~ all(is.na(.x)))
    if (any(empty_unnamed)) {
      message("Removed empty unnamed columns: ", paste(names(data)[empty_unnamed], collapse = ", "))
      data <- data[, !empty_unnamed, drop = FALSE]
    }
  }
  data
}
```

## Load data

There are **1 CSV distribution(s)**. Each is loaded into `df` in turn; the analysis uses the last one. Run only the assignment you need to analyze another distribution.

The delimiter and column types are guessed. Check the preview and metadata; set `delim`, `col_types`, `na`, or `locale` in `get_dataset(...)` when needed (for example, read identifiers with leading zeros as character columns). Parsing problems stop the import so they can be addressed.

Fully empty columns named `...n` are removed on import. Named empty columns and unnamed columns containing values are kept. Use `drop_empty_unnamed = FALSE` to retain every column, including intentionally named `...n` fields.

```{r load-data}
# Distribution 0
# Ktzhdistid               : 6183
# Title                    : Baugesuche im Kanton Zürich
# Description              : Für eine Beschreibung der einzelnen Variablen siehe "weitere Informationen" auf der Startseite des Datensatzes.
# Issued                   : 2025-06-24T22:00:00
# Modified                 : 2026-09-27T01:45:24

df <- get_dataset('https://daten.statistik.zh.ch/ogd/daten/ressourcen/KTZH_00002982_00006183.csv')


```

## Overview

Inspect before cleaning: these chunks leave `df` unchanged. Duplicate rows and missing values may be meaningful.

```{r overview}
tibble(
  rows = nrow(df),
  columns = ncol(df),
  duplicate_rows_after_first = sum(duplicated(df))
)
glimpse(df)
head(df)
```

## Missing values

```{r missing-values}
missing <- tibble(
  column = names(df),
  missing = map_int(df, ~ sum(is.na(.x))),
  missing_pct = map_dbl(df, ~ mean(is.na(.x)) * 100)
) |>
  arrange(desc(missing_pct))
missing

# Show up to 20 columns with missing values; percentages use all rows.
missing_plot <- missing |> filter(missing > 0) |> slice_head(n = 20)
if (nrow(missing_plot) > 0) {
  ggplot(missing_plot, aes(x = missing_pct, y = reorder(column, missing_pct))) +
    geom_col(fill = "steelblue") +
    scale_x_continuous(limits = c(0, 100)) +
    labs(x = "Missing values (%)", y = NULL, title = "Missingness by column")
} else {
  message("No missing values to plot (or the dataset has no rows).")
}
```

## Summary and distributions

`skim()` reports completeness and type-specific summaries. Inspect units before interpreting numeric codes as measurements.

```{r summary}
if (nrow(df) > 0 && ncol(df) > 0) {
  skim(df)
} else {
  message("No data to summarize.")
}
```

```{r histograms}
# Plot up to four numeric columns, excluding non-finite values only from plots.
numeric_names <- names(select(df, where(is.numeric))) |> head(4)
for (column in numeric_names) {
  values <- df[[column]]
  values <- values[is.finite(values)]
  if (length(values) > 0) {
    plot <- ggplot(tibble(value = values), aes(x = value)) +
      geom_histogram(bins = 30, fill = "steelblue", colour = "white") +
      labs(title = column, x = column, y = "Count")
    print(plot)
  }
}
```

```{r category-counts}
# Top 10 values for up to three categorical columns, including missing values.
categorical_names <- df |>
  select(where(~ is.character(.x) || is.factor(.x) || is.logical(.x))) |>
  names() |>
  head(3)
for (column in categorical_names) {
  cat(column, "\n")
  df |> count(.data[[column]], sort = TRUE) |> head(10) |> print()
}
```

## Next steps

Choose columns from `names(df)` and adapt these examples. Use the metadata to decide which comparisons make sense.

```{r next-steps}
# Group summary (replace column names):
# df |> summarise(n = n(), mean = mean(value, na.rm = TRUE), .by = group)

# Parse a date explicitly, then inspect a time trend:
# dated <- df |> mutate(date = parse_date(date, format = "%Y-%m-%d"))
# dated |> ggplot(aes(x = date, y = value)) + geom_point()

# Relationship between two numeric variables:
# df |> ggplot(aes(x = x_column, y = y_column)) + geom_point(alpha = 0.5)
```

## Questions about the data?

Amt für Statistik und Daten | Data Shop | datashop@statistik.zh.ch
