---
title: "Open Government Data, provided by Canton Zurich"
date: "2023-09-14"
output: html_document
---

## Dataset: COVID_19 open government data reported by Swiss Cantons and Principality of Liechtenstein from January 5, 2020

Data is generated and validated daily using manual and automated procedures. Note that we only publish data that are reported by the Swiss Cantons and the Principality of Liechtenstein. Thus, gaps result if Swiss Cantons or the Principality of Liechtenstein do not report data for a specific date. Updates of cantonal case numbers during weekends are infrequent.

[Direct data shop link for dataset](https://www.zh.ch/de/politik-staat/opendata.html#/datasets/673@fachstelle-ogd-kanton-zuerich)

Auto generated R starter code for data set 673@fachstelle-ogd-kanton-zuerich.

## Metadata

- **Issued** `2020-03-16T07:46:00`
- **Modified** `2023-01-10T17:08:07`
- **Startdate** `2020-01-05`
- **Enddate** `None`
- **Theme** `['Gesundheit']`
- **Keyword** `['gesundheit', 'kantone', 'krankheiten', 'schweiz', 'corona', 'covid-19', 'sars-cov-2', 'covid19', 'ogd']`
- **Publisher** `['Fachstelle Open Government Data des Kantons Zürich']`
- **Landingpage** `https://github.com/openZH/covid_19/`


# Load packages

```{r}

library(tidyverse)
library(skimr)

```

# Load data

-   The dataset has 1 distribution(s) in CSV format.
-   All available CSV distributions are listed below and can be read into a tibble.

```{r}

# Distribution 0
# Ktzhdistid               : 1627
# Title                    : COVID_19 open government data reported by Swiss Cantons and Principality of Liechtenstein from January 5, 2020
# Description              : Case numbers include persons tested in Switzerland per Canton (26 Cantons) plus Principality of Liechtenstein. For definition of variables see Readme listed below "Further information / Weitere Informationen".
# Issued                   : 2020-03-16T08:05:32
# Modified                 : 2021-07-06T14:33:17
# Rights                   : NonCommercialAllowed-CommercialAllowed-ReferenceRequired

df <- read_delim('https://raw.githubusercontent.com/openZH/covid_19/master/COVID19_Fallzahlen_CH_total_v2.csv')



```

# Analyze data

```{r}

glimpse(df)
str(df)
skim(df)

head(df)
tail(df)

```

# Continue your code here...

```{r}

```

------------------------------------------------------------------------

# Questions about the data?

Fachstelle Open Government Data des Kantons Zürich | info@open.zh.ch
